NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PS lipids

### 2019-02-18 Manuscript/manuscriptPS.tex
Update manuscript pdf

POPC:POPS (5:1)/K$^{+}$  & MacRog \cite{maciejewski14}  & 0  & 120 & 5760  & 0  & 298  & 400 \todo{lenght wrong? Check zenodo} & 250 \todo{lenght wrong? Check zenodo} &  \todo{this ref is to trajectory with CA}\cite{POPCpopsMACROG}\tabularnewline

>>>>

POPC:POPS (5:1)/K$^{+}$  & MacRog \cite{maciejewski14}  & 0  & 120 & 5760  & 0  & 298  & 400 \todoi{lenght wrong? Check zenodo} & 250 \todoi{lenght wrong? Check zenodo} &  \todoi{this ref is to trajectory with CA}\cite{POPCpopsMACROG}\tabularnewline
